
---
title: "Allele-specific Expression"
author: "Heath O'Brien"
output:
  tufte::tufte_html: default
  '#tufte::tufte_handout': default
---
<!-- see http://rstudio.github.io/tufte/ for info about tufte -->
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warnings=FALSE, message = FALSE, dev.args = list(bg = 'transparent'))

library(ggplot2)
library(dplyr)
library(tidyr)
library(readr)
library(tufte)
rm(list=ls())
source("~/BTSync/FetalRNAseq/LabNotes/R/ASexpressionFunctions.R")
```

#AS3MT (Deduplicated, Clipped)

`r margin_note("- There appear to be two cases of samples with the incorrect genotype (one T|T genotype with 55% C and one T|C genotype with 100% C (3 others have very low read counts)")`

```{r }
count_file <- "~/BTSync/FetalRNAseq/Counts/AlleleSpecific/chr10:102901727-102901727.clip.counts.txt"
riskVar_file <- "~/BTSync/FetalRNAseq/Genotypes/rs11191419.txt"
ExpressedSNP_file <- "~/BTSync/FetalRNAseq/Genotypes/rs1046778.txt"
counts<-GetCounts(count_file, riskVar_file, ExpressedSNP_file)

PlotASE(counts)
```
`r margin_note("- If 16972 (het with 16 C to 0 T) is excluded, difference is ALMOST significant (p=0.0565))")`
`r margin_note("- Removing T|T homozygotes makes no difference")`
`r margin_note("- After adding additional samples, result is non significant")`

```{r }
hets <- filter(counts, ExpressedSNP == 'C|T' | ExpressedSNP == 'T|C') %>% 
  mutate(riskVar = ifelse(riskVar == 'T|A', 'A|T', as.character(riskVar)))

PlotDistortion(hets)
PlotRatio(hets)
summary(glm(cbind(alt, ref) ~ riskVar, data=hets, family = binomial))
summary(glm(cbind(alt, ref) ~ riskVar, data=filter(hets, sample != 16972), family = binomial))
summary(glm(cbind(alt, ref) ~ riskVar, data=filter(hets, sample != 16972 & riskVar != 'T|T'), family = binomial))

```

`r margin_note("- All Samples from Duarte et al. that have been sequenced are genotyped as heterozygotes for the expressed SNP")`
`r margin_note("- 16972 is one of the samples that was identified as a sample swap. 16115 appears to be correct")`
```{r }
SNAPshotExpression <- read_tsv("~/BTSync/FetalRNAseq/Info/ASMT.txt", 
                    col_names=T,
                    col_types = cols(sample="c", rs1046778="d")
                    )
left_join(SNAPshotExpression, hets) %>% 
  ggplot(aes(x=rs1046778, y=ref/alt, size=ref+alt)) +
  geom_point() + 
  geom_text(aes(label=sample), size=5, hjust=-.2) + 
  geom_abline(slope=1, intercept = 0) +
  tufte_theme()
```


```{r }
SNAPshot <- read_tsv("~/BTSync/FetalRNAseq/Info/SNAPshot.txt", 
                    col_names=T,
                    col_types = cols(ID="c", 
                                     rs4917985="c", 
                                     rs1046778="c", 
                                     rs2275271="c", 
                                     rs3740387="c"
                                     )
                    )

counts2 <- separate(counts, ExpressedSNP, c("a", "b")) %>% mutate(ExpressedSNP= paste(a,b, sep=''))
counts2 <- left_join(counts2, SNAPshot, by = c("sample" = "ID")) %>% 
  mutate(match = ifelse(ExpressedSNP == rs1046778, 'match', 'mismatch')) %>%
  mutate(match = ifelse(rs1046778 == 'CT' & ExpressedSNP == 'TC', 'match', match))
ggplot(counts2, aes(x=riskVar, y=alt/(ref+alt), size=ref+alt, colour = match)) +
  geom_jitter(alpha=.2, height=0, width=.25) +
  facet_grid(ExpressedSNP ~ .) +
  scale_y_continuous(limits=c(-.1, 1.1), breaks=c(0,.2,.4,.6,.8,1)) +
  ylab('% Alternate Allele') +
  xlab('GWAS Risk Variant') +
  tufte_theme() +
  theme(legend.position="top")
```


#MIR137HG (Deduplicated, Clipped)

`r margin_note("- All Expressed SNP but one are hets are heterozygous for risk var")`

```{r }
count_file <- "~/BTSync/FetalRNAseq/Counts/AlleleSpecific/chr1:98046571-98046571.clip.counts.txt"
riskVar_file <- "~/BTSync/FetalRNAseq/Genotypes/rs1625579.txt"
ExpressedSNP_file <- "~/BTSync/FetalRNAseq/Genotypes/rs2660304.txt"
counts<-GetCounts(count_file, riskVar_file, ExpressedSNP_file)
PlotASE(counts)

hets <- filter(counts, ExpressedSNP == 'G|T' | ExpressedSNP == 'T|G') %>% 
  mutate(riskVar = ifelse(riskVar == 'T|G', 'G|T', as.character(riskVar)))

PlotDistortion(hets)
PlotRatio(hets)
summary(glm(cbind(alt, ref) ~ riskVar, data=hets, family = binomial))

```


#PCGEM1 (Deduplicated, Clipped)

`r margin_note("- Expressed at VERY low levels in developing brain")`

```{r }
count_file <- "~/BTSync/FetalRNAseq/Counts/AlleleSpecific/chr2:192775750-192775750.clip.counts.txt"
riskVar_file <- "~/BTSync/FetalRNAseq/Genotypes/rs17662626.txt"
ExpressedSNP_file <- "~/BTSync/FetalRNAseq/Genotypes/rs13419834.txt"
counts<-GetCounts(count_file, riskVar_file, ExpressedSNP_file)

PlotASE(counts)

hets <- filter(counts, ExpressedSNP == 'C|T' | ExpressedSNP == 'T|C') %>% 
  mutate(riskVar = ifelse(riskVar == 'G|A', 'A|G', as.character(riskVar)))

PlotDistortion(hets)
PlotRatio(hets)
summary(glm(cbind(alt, ref) ~ riskVar, data=hets, family = binomial))

```

#TRIM26 (Deduplicated, Clipped)

`r margin_note("- Alternate allele has significnatly higher expression independent of risk SNP")`

```{r }
count_file <- "~/BTSync/FetalRNAseq/Counts/AlleleSpecific/chr6:30186422-30186422.clip.counts.txt"
riskVar_file <- "~/BTSync/FetalRNAseq/Genotypes/rs2021722.txt"
ExpressedSNP_file <- "~/BTSync/FetalRNAseq/Genotypes/rs2074473.txt"
counts<-GetCounts(count_file, riskVar_file, ExpressedSNP_file)
PlotASE(counts)

hets <- filter(counts, ExpressedSNP == 'C|T' | ExpressedSNP == 'T|C') %>% 
  mutate(riskVar = ifelse(riskVar == 'T|C', 'C|T', as.character(riskVar)))

PlotDistortion(hets)
PlotRatio(hets)
summary(glm(cbind(alt, ref) ~ riskVar, data=hets, family = binomial))
```


#CSMD1 (Deduplicated, Clipped)

`r margin_note("- Non-significant")`

```{r }
count_file <- "~/BTSync/FetalRNAseq/Counts/AlleleSpecific/chr8:2937908-2937908.clip.counts.txt"
riskVar_file <- "~/BTSync/FetalRNAseq/Genotypes/rs10503253.txt"
ExpressedSNP_file <- "~/BTSync/FetalRNAseq/Genotypes/rs2291319.txt"
counts<-GetCounts(count_file, riskVar_file, ExpressedSNP_file)
PlotASE(counts)

hets <- filter(counts, ExpressedSNP == 'G|T' | ExpressedSNP == 'T|G') %>% 
  mutate(riskVar = ifelse(riskVar == 'C|A', 'A|C', as.character(riskVar)))

PlotDistortion(hets)
PlotRatio(hets)
summary(glm(cbind(alt, ref) ~ riskVar, data=hets, family = binomial))
```


#MMP16  (Deduplicated, Clipped)
`r margin_note("- Non-significant")`

```{r }
count_file <- "~/BTSync/FetalRNAseq/Counts/AlleleSpecific/chr8:88039069-88039069.clip.counts.txt"
riskVar_file <- "~/BTSync/FetalRNAseq/Genotypes/rs7004633.txt"
ExpressedSNP_file <- "~/BTSync/FetalRNAseq/Genotypes/rs2664370.txt"
counts<-GetCounts(count_file, riskVar_file, ExpressedSNP_file)
PlotASE(counts)

hets <- filter(counts, ExpressedSNP == 'C|T' | ExpressedSNP == 'T|C') %>% 
  mutate(riskVar = ifelse(riskVar == 'G|A', 'A|G', as.character(riskVar)))

PlotDistortion(hets)
PlotRatio(hets)
summary(glm(cbind(alt, ref) ~ riskVar, data=hets, family = binomial))

```


#CNNM2 (deduplicated, clipped)
`r margin_note("- All samples that are heterozygose for the expressed SNP are also heterozygous for the risk SNP")`

```{r }
count_file <- "~/BTSync/FetalRNAseq/Counts/AlleleSpecific/chr10:103054405-103054405.clip.counts.txt"
riskVar_file <- "~/BTSync/FetalRNAseq/Genotypes/rs7914558.txt"
ExpressedSNP_file <- "~/BTSync/FetalRNAseq/Genotypes/rs2275271.txt"
counts<-GetCounts(count_file, riskVar_file, ExpressedSNP_file)
PlotASE(counts)

hets <- filter(counts, ExpressedSNP == 'C|T' | ExpressedSNP == 'T|C') %>% 
  mutate(riskVar = ifelse(riskVar == 'G|A', 'A|G', as.character(riskVar)))

PlotDistortion(hets)
PlotRatio(hets)
#summary(glm(cbind(alt, ref) ~ riskVar, data=hets, family = binomial))

```

#NT5C2 (deduplicated, clipped)
`r margin_note("- Risk variant is very rare")`
`r margin_note("- Slight decrease in alt allele, which is significant")`

```{r }
count_file <- "~/BTSync/FetalRNAseq/Counts/AlleleSpecific/chr10:103089711-103089711.clip.counts.txt"
riskVar_file <- "~/BTSync/FetalRNAseq/Genotypes/rs11191580.txt"
ExpressedSNP_file <- "~/BTSync/FetalRNAseq/Genotypes/rs3740387.txt"
counts<-GetCounts(count_file, riskVar_file, ExpressedSNP_file)
PlotASE(counts)

hets <- filter(counts, ExpressedSNP == 'A|G' | ExpressedSNP == 'G|A') %>% 
  mutate(riskVar = ifelse(riskVar == 'T|C', 'C|T', as.character(riskVar)))

PlotDistortion(hets)
PlotRatio(hets)
hets$riskVar <- relevel(factor(hets$riskVar), 'T|T')
summary(glm(cbind(alt, ref) ~ riskVar, data=hets, family = binomial))
```

#STT3A (deduplicated, clipped)
`r margin_note("- Risk variant is rare, but hets have significantly lower expression of alt allele")`

```{r }
count_file <- "~/BTSync/FetalRNAseq/Counts/AlleleSpecific/chr11:125609468-125609468.clip.counts.txt"
riskVar_file <- "~/BTSync/FetalRNAseq/Genotypes/rs548181.txt"
ExpressedSNP_file <- "~/BTSync/FetalRNAseq/Genotypes/rs2241502.txt"
counts<-GetCounts(count_file, riskVar_file, ExpressedSNP_file)
PlotASE(counts)

hets <- filter(counts, ExpressedSNP == 'A|G' | ExpressedSNP == 'G|A') %>% 
  mutate(riskVar = ifelse(riskVar == 'G|A', 'A|G', as.character(riskVar)))

PlotDistortion(hets)
PlotRatio(hets)
summary(glm(cbind(alt, ref) ~ riskVar, data=hets, family = binomial))
```


#CCDC68 (deduplicated, clipped)
`r margin_note("- Counts are low")`

`r margin_note("- Differences are not significant")`
```{r }
count_file <- "~/BTSync/FetalRNAseq/Counts/AlleleSpecific/chr18:54903114-54903114.clip.counts.txt"
riskVar_file <- "~/BTSync/FetalRNAseq/Genotypes/rs12966547.txt"
ExpressedSNP_file <- "~/BTSync/FetalRNAseq/Genotypes/rs1944362.txt"
counts<-GetCounts(count_file, riskVar_file, ExpressedSNP_file)
PlotASE(counts)

hets <- filter(counts, ExpressedSNP == 'A|C' | ExpressedSNP == 'C|A') %>% 
  mutate(riskVar = ifelse(riskVar == 'G|A', 'A|G', as.character(riskVar)))

PlotDistortion(hets)
PlotRatio(hets)
summary(glm(cbind(alt, ref) ~ riskVar, data=hets, family = binomial))

```


#TCF4 (deduplicated, clipped)

`r margin_note("- risk allele is EXTREMELY rare")`

```{r }
count_file <- "~/BTSync/FetalRNAseq/Counts/AlleleSpecific/chr18:55228300-55228300.clip.counts.txt"
riskVar_file <- "~/BTSync/FetalRNAseq/Genotypes/rs17512836.txt"
ExpressedSNP_file <- "~/BTSync/FetalRNAseq/Genotypes/rs8766.txt"
counts<-GetCounts(count_file, riskVar_file, ExpressedSNP_file)
PlotASE(counts)

hets <- filter(counts, ExpressedSNP == 'T|C' | ExpressedSNP == 'C|T') %>% 
  mutate(riskVar = ifelse(riskVar == 'T|C', 'C|T', as.character(riskVar)))

PlotDistortion(hets)
PlotRatio(hets)
summary(glm(cbind(alt, ref) ~ riskVar, data=hets, family = binomial))
```