---
title: "Alignment QC"
author: "Heath O'Brien"
output:
  tufte::tufte_html: default
  #tufte::tufte_handout: default
---
<!-- see http://rstudio.github.io/tufte/ for info about tufte -->
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyr)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(RColorBrewer)
library(tufte)
rm(list=ls())
source("~/BTSync/Code/R/FormatGGplot.R")
folders <- c("/Users/heo3/BTSync/FetalRNAseq/BamQC/Carolina/034_96_CER_S9",
             #"/Users/heo3/BTSync/FetalRNAseq/BamQC/Carolina/034_96_T_ctx_S13",
             "/Users/heo3/BTSync/FetalRNAseq/BamQC/Carolina/038_95_CER_S10",
             "/Users/heo3/BTSync/FetalRNAseq/BamQC/Carolina/038_95_T_ctx_S14",
             "/Users/heo3/BTSync/FetalRNAseq/BamQC/Carolina/209_13_CER_S11",
             "/Users/heo3/BTSync/FetalRNAseq/BamQC/Carolina/209_13_T_ctx_S15",
             "/Users/heo3/BTSync/FetalRNAseq/BamQC/Carolina/407_13_CER_S12",
             "/Users/heo3/BTSync/FetalRNAseq/BamQC/Carolina/407_13_T_ctx_S16"
             )
```

# RSeQC
## Mapping Stats
`r margin_note("- rDNA reads not included in first three stats")`
`r margin_note("- # uniquely mapped reads ranges from 126 million to 230 million, with 3 samples (17054, 17160, 15483) having < 100 million")`
`r margin_note("- Between 36% and 55% are properly paired")`
`r margin_note("- % rRNA ranges from 0.1% to 5%")`

``` {r }
RSeQCstats <- data.frame()
for (folder in folders) {
  print(folder)
  temp <- read.delim(paste(folder, ".chr.stats.txt", sep=""), 
                     header=FALSE, stringsAsFactors=FALSE, skip=5, sep=':'
                     )
  temp[4,2] <-strsplit(temp[4,1], ' +')[[1]][4]
  temp[4,1] <- 'Non primary hits'
  temp <- temp[c(6,7,14),]
  temp2 <- read.delim(paste(folder, ".in.stats.txt", sep=""), 
                     header=FALSE, stringsAsFactors=FALSE, skip=5, sep=':'
                     )
  temp2[4,2] <-strsplit(temp[4,1], ' +')[[1]][4]
  temp2[4,1] <- 'Non primary hits'
  temp <-rbind(temp, c("rDNA",sum(as.numeric(temp2[c(6,7),2]))))
  temp[,1] <- c("Multimapped", "Unique", "Paired", "rDNA")
  temp$sample <- tail(strsplit(folder, '/')[[1]], 1)
  RSeQCstats <- rbind(RSeQCstats, temp)
}
RSeQCstats <- spread(RSeQCstats, V1, V2)
#mutate(RSeQCstats, Perc_rDNA = as.numeric(rDNA)/(as.numeric(Unique)+as.numeric(Multimapped)+as.numeric(rDNA))) %>% arrange(Perc_rDNA)
ReadNumbers <- RSeQCstats[,c(1,5)]
RSeQCstats <- RSeQCstats[c(1,5,3,2,4)]
RSeQCstats[,2:5] <- sapply(RSeQCstats[,2:5], function(x) formatC(as.numeric(x), format='d', big.mark=','))
knitr::kable(
  RSeQCstats
)
```


## Distribution of Reads Among Features (proportion of tags mapping to different feature classes)
`r margin_note("- Intergenic only considers sequence within 10 kb upstream of TSS and downstream of TES")`
`r margin_note("- These numbers look very similar to the older data")`


``` {r }
RSeQCdistribution <- data.frame()
ReadNumbers$ExpressedTags = NA
for (folder in folders) {
  sample <- tail(strsplit(folder, '/')[[1]], 1)
  temp <- read.delim(paste(folder, ".dist.txt", sep=""), 
                           header=TRUE, stringsAsFactors=FALSE, skip=4, sep=''
                     )
  temp <- temp[-11,]
  tag_total <- sum(temp[c(1,2,3,4,7,10),3])
  ReadNumbers[ReadNumbers$sample == sample,]$ExpressedTags <- sum(temp[c(1,2,3),3])
  temp <- data.frame(V1 = c("Tags_per_read", "CDS", "UTR", "Intron", "Intergenic"), 
                     V2=c(
                  tag_total/as.numeric(ReadNumbers[ReadNumbers$sample == sample,]$Unique),
                  temp[1,3]/tag_total, 
                  sum(as.numeric(temp[c(2,3),3]))/tag_total,
                  temp[4,3]/tag_total,
                  sum(as.numeric(temp[c(7,10),3]))/tag_total
                  )
             )
  temp$sample <- sample
  RSeQCdistribution <- rbind(RSeQCdistribution, temp)
}
RSeQCdistribution <- spread(RSeQCdistribution, V1, V2)
RSeQCdistribution <- RSeQCdistribution[c(1,5,2,6,4,3)]

knitr::kable(
  RSeQCdistribution
)
```

## Strand

`r margin_note("- Data consistent with second-strand experiment")`

```{r }
RSeQCstats <- data.frame()
for (folder in folders) {
  temp <- read.delim(paste(folder, ".expt.txt", sep=""), 
                     skip=3, header=FALSE, sep=':'
                     )
  temp$sample <- tail(strsplit(folder, '/')[[1]], 1)
  temp$V1 <- c("Ambiguous", "First Strand", "Second Strand")
  RSeQCstats <- rbind(RSeQCstats, temp)
}
RSeQCstats <- spread(RSeQCstats, V1, V2)

knitr::kable(
  RSeQCstats
)
```

## Insert Size Distribution

`r margin_note("- Insert size centred on 0 bp")`
`r margin_note("- Since these are 75 bp reads, that indicates fragment sizes centred on 150 bp")`
`r margin_note("- This indicates that fragment size tends to be around 125-150 bp")`


```{r include=FALSE}
RSeQCstats <- data.frame()
for (folder in folders) {
  #print(folder)
  temp <- read.delim(paste(folder, ".inner_distance_freq.txt", sep=""),
                     header=FALSE
                     )
  sample <- tail(strsplit(folder, '/')[[1]], 1)
  temp$sample <- sample
  RSeQCstats <- rbind(RSeQCstats, temp)
}
```

```{r dev.args = list(bg = 'transparent')}
ggplot(RSeQCstats, aes(x=(V1+V2)/2, y=V3, colour=sample, group=sample)) +
  geom_line() +
  ylab('reads') +
  xlab('inner distance') +
  theme(legend.position=c(.8,.8)) +
  scale_colour_brewer(type = "qual", palette = 6) +
  tufte_theme() 

```

## Transcript Read Coverage

`r margin_note("- Looks good. Steep drop-offs at the ends, especially 5'")`
`r margin_note("- I'm still a bit surprised about the spread in these values because I've normalised by the number of tags that map to CDS or UTR features. I guess there can be some variation in the size of the tags, but this still seems like a lot")`

```{r dev.args = list(bg = 'transparent')}
RSeQCstats <- data.frame()
for (folder in folders) {
  #print(folder)
  temp <- read.delim(paste(folder, ".geneBodyCoverage.txt", sep=""),
                     header=FALSE
                     )
  temp <-  as.data.frame(t(temp[,-1]))
  sample <- tail(strsplit(folder, '/')[[1]], 1)
  temp$sample <- sample
  temp$V2 <- temp$V2
  temp$ReadNumbers <- as.numeric(ReadNumbers[ReadNumbers$sample == sample,]$ExpressedTags)
  RSeQCstats <- rbind(RSeQCstats, temp)
}

ggplot(RSeQCstats, aes(x=V1, y=V2/ReadNumbers, colour=sample, group=sample)) +
  geom_line() +
  ylab('reads') +
  tufte_theme() +
  theme(legend.position=c(0.1,.9)) +
  scale_colour_brewer(type = "qual", palette = 6) +
  xlab('transcript percentile') +
  ylab("proportion of expressed tags")
  
```

## Sequence Duplication

`r margin_note("- Plenty of duplication")`
`r margin_note("- Probably not unexpected in this case")`
`r margin_note("- Duplication higher for Exeter samples")`

```{r include=FALSE}
RSeQCstats <- data.frame()
for (folder in folders) {
  eval(parse(file = paste(folder, ".DupRate_plot.r", sep=""))[2:6])
  temp <- rbind(data.frame(Reads=pos_uniqRead, 
                            Duplication_level=pos_occ, 
                            Method='Position-based'
                            ),
                 data.frame(Reads=seq_uniqRead, 
                            Duplication_level=seq_occ, 
                            Method='Sequence-based'
                            )
                )
  sample <- tail(strsplit(folder, '/')[[1]], 1)
  temp$sample <- sample
  temp$ReadNumbers <- as.numeric(ReadNumbers[ReadNumbers$sample == sample,]$Unique)
  RSeQCstats <- rbind(RSeQCstats, temp)
}

```

```{r dev.args = list(bg = 'transparent'), warning=FALSE}
ggplot(RSeQCstats, aes(x=Duplication_level, y=Reads/ReadNumbers, colour=sample, group=sample)) +
  geom_point(alpha=.2) +
  xlim(c(0,500)) +
  scale_y_log10() +
  tufte_theme() +
  theme(legend.position=c(.8,.8)) +
  scale_colour_brewer(type = "qual", palette = 6) +
  facet_wrap(~ Method) +
  ylab("Proportion of Reads")


```

## Splice Junction Saturation

`r margin_note("- It looks like both known and novel splice sites continue to be found")`

```{r include=FALSE}
RSeQCstats <- data.frame()
for (folder in folders) {
  eval(parse(file = paste(folder, ".junctionSaturation_plot.r", sep=""))[2:5])
  temp<-rbind(
              data.frame(percent_reads=x, junctions=z, Category='All'),
              data.frame(percent_reads=x, junctions=y, Category='Known'),
              data.frame(percent_reads=x, junctions=w, Category='Novel')
              )
  sample <- tail(strsplit(folder, '/')[[1]], 1)
  temp$sample <- sample
  temp$ReadNumbers <- as.numeric(ReadNumbers[ReadNumbers$sample == sample,2])
  RSeQCstats <- rbind(RSeQCstats, temp)
}

```

```{r dev.args = list(bg = 'transparent'), warning=FALSE}
ggplot(RSeQCstats, aes(y=junctions, x=ReadNumbers*percent_reads/100, group=sample, colour=sample)) +
  geom_point() +
  #xlim(c(0,500)) +
  #scale_y_log10() +
  scale_colour_brewer(type = "qual", palette = 6) +
  tufte_theme() +
  theme(legend.position=c(.8,.9)) +
  facet_wrap(~ Category, scales='free') +
  xlab("Number of Reads")

```

## Mutation Distribution

