
---
title: "ZNF804A"
author: "Heath O'Brien"
output:
  tufte::tufte_html: default
  #tufte::tufte_handout: default
---
<!-- see http://rstudio.github.io/tufte/ for info about tufte -->
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warnings=FALSE, message = FALSE, dev.args = list(bg = 'transparent'))

library(ggplot2)
library(dplyr)
library(tidyr)
library(readr)
library(tufte)
rm(list=ls())
source("~/BTSync/Code/R/FormatGGplot.R")
allCounts <- read_tsv("~/BTSync/FetalRNAseq/Counts/tables/num2vsnum1.complete.txt")
covariates <- read_tsv("~/BTSync/FetalRNAseq/Info/sample_info.txt")

```

#AS3MT
## Overall expression
`r margin_note("- DESeq-normalized counts")`
`r margin_note("- Heterzygotes are combined in this analysis")`
`r margin_note("- Used raw tophat output (without running WASP)")`

```{r }
riskVar <- read.delim("~/BTSync/FetalRNAseq/Genotypes/rs11191419.txt", header=FALSE)
colnames(riskVar) <- c('chr', 'pos', 'riskVar', 'BrainBankID')
counts<- allCounts[,c(1, 79:155)] %>%
  filter(Id =='ENSG00000214435.7') %>%
  gather(sample, count, -Id) %>%
  separate(sample, c('norm', 'BrainBankID'), sep='\\.') %>%
  left_join(riskVar) %>%
  mutate(riskVar = ifelse(riskVar == 'T|A', 'A|T', as.character(riskVar)))

ggplot(counts, aes(x=riskVar, y=count)) +
  geom_jitter(alpha=.2, height=0, width=.25) +
  tufte_theme()

summary(lm(count ~ riskVar, data=counts))
```

## Co-variates
`r margin_note("- ")`

```{r}
count_cov <- counts %>% left_join(covariates) 
ggplot(count_cov, aes(x=PCW, y=count)) + geom_point(alpha=.2) +
  tufte_theme()
ggplot(count_cov, aes(x=Sex, y=count)) +   geom_jitter(alpha=.2, height=0, width=.25) +
  tufte_theme()
ggplot(count_cov, aes(x=RIN, y=count)) + geom_point(alpha=.2) +
  tufte_theme()

summary(lm(count ~ riskVar + PCW + Sex + RIN, data=count_cov))
summary(lm(count ~ PCW, data=count_cov))
summary(lm(count ~ Sex, data=count_cov))
summary(lm(count ~ RIN, data=count_cov))
cor.test(count_cov$count, count_cov$PCW)
cor.test(count_cov$count, count_cov$RIN)
```

#ZNF804A
## Overall expression
`r margin_note("- DESeq-normalized counts")`
`r margin_note("- Heterzygotes are combined in this analysis")`
`r margin_note("- Used raw tophat output (without running WASP)")`

```{r }
riskVar <- read.delim("~/BTSync/FetalRNAseq/Genotypes/rs1344706.txt", header=FALSE)
colnames(riskVar) <- c('chr', 'pos', 'riskVar', 'BrainBankID')
counts<- allCounts[,c(1, 79:155)] %>%
  filter(Id =='ENSG00000170396.7') %>%
  gather(sample, count, -Id) %>%
  separate(sample, c('norm', 'BrainBankID'), sep='\\.') %>%
  left_join(riskVar) %>%
  mutate(riskVar = ifelse(riskVar == 'C|A', 'A|C', as.character(riskVar)))

ggplot(counts, aes(x=riskVar, y=count)) +
  geom_jitter(alpha=.2, height=0, width=.25) +
  tufte_theme()

summary(lm(count ~ riskVar, data=counts))
```


## Co-variates
`r margin_note("- ZNF804A is nagatively correlated with RIN")`

```{r}
count_cov <- counts %>% left_join(covariates) 
ggplot(count_cov, aes(x=PCW, y=count)) + geom_point(alpha=.2) +
  tufte_theme()
ggplot(count_cov, aes(x=Sex, y=count)) +   geom_jitter(alpha=.2, height=0, width=.25) +
  tufte_theme()
ggplot(count_cov, aes(x=RIN, y=count)) + geom_point(alpha=.2) +
  tufte_theme()

summary(lm(count ~ PCW + Sex +RIN, data=count_cov))
summary(lm(count ~ PCW, data=count_cov))
summary(lm(count ~ Sex, data=count_cov))
summary(lm(count ~ RIN, data=count_cov))
cor.test(count_cov$count, count_cov$PCW)
cor.test(count_cov$count, count_cov$RIN)
```

#MIR137HG

```{r }
riskVar <- read.delim("~/BTSync/FetalRNAseq/Genotypes/rs1625579.txt", header=FALSE)
colnames(riskVar) <- c('chr', 'pos', 'riskVar', 'BrainBankID')
counts<- allCounts[,c(1, 79:155)] %>%
  filter(Id =='ENSG00000225206.5') %>%
  gather(sample, count, -Id) %>%
  separate(sample, c('norm', 'BrainBankID'), sep='\\.') %>%
  left_join(riskVar) %>%
  mutate(riskVar = ifelse(riskVar == 'T|G', 'G|T', as.character(riskVar)))

ggplot(counts, aes(x=riskVar, y=count)) +
  geom_jitter(alpha=.2, height=0, width=.25) +
  tufte_theme()

summary(lm(count ~ riskVar, data=counts))
```


## Co-variates
`r margin_note("- MIR137HG is positively correlated with PCW")`

```{r}
count_cov <- counts %>% left_join(covariates) 
ggplot(count_cov, aes(x=PCW, y=count)) + geom_point(alpha=.2) +
  tufte_theme()
ggplot(count_cov, aes(x=Sex, y=count)) +   geom_jitter(alpha=.2, height=0, width=.25) +
  tufte_theme()
ggplot(count_cov, aes(x=RIN, y=count)) + geom_point(alpha=.2) +
  tufte_theme()

summary(lm(count ~ PCW + Sex +RIN, data=count_cov))
summary(lm(count ~ PCW, data=count_cov))
summary(lm(count ~ Sex, data=count_cov))
summary(lm(count ~ RIN, data=count_cov))
cor.test(count_cov$count, count_cov$PCW)
cor.test(count_cov$count, count_cov$RIN)
```


#PCGEM1
`r margin_note("- Expressed at VERY low levels in developing brain")`

```{r }
riskVar <- read_tsv("~/BTSync/FetalRNAseq/Genotypes/rs17662626.txt", col_names=FALSE)
colnames(riskVar) <- c('chr', 'pos', 'riskVar', 'BrainBankID')
counts<- allCounts[,c(1, 79:155)] %>%
  filter(Id =='ENSG00000227418.6') %>%
  gather(sample, count, -Id) %>%
  separate(sample, c('norm', 'BrainBankID'), sep='\\.') %>%
  left_join(riskVar) %>%
  mutate(riskVar = ifelse(riskVar == 'G|A', 'A|G', as.character(riskVar)))

ggplot(counts, aes(x=riskVar, y=count)) +
  geom_jitter(alpha=.2, height=0, width=.25) +
  tufte_theme()

summary(lm(count ~ riskVar, data=counts))
```


## Co-variates

```{r}
count_cov <- counts %>% left_join(covariates) 
ggplot(count_cov, aes(x=PCW, y=count)) + geom_point(alpha=.2) +
  tufte_theme()
ggplot(count_cov, aes(x=Sex, y=count)) +   geom_jitter(alpha=.2, height=0, width=.25) +
  tufte_theme()
ggplot(count_cov, aes(x=RIN, y=count)) + geom_point(alpha=.2) +
  tufte_theme()

summary(lm(count ~ PCW + Sex +RIN, data=count_cov))
summary(lm(count ~ PCW, data=count_cov))
summary(lm(count ~ Sex, data=count_cov))
summary(lm(count ~ RIN, data=count_cov))
cor.test(count_cov$count, count_cov$PCW)
cor.test(count_cov$count, count_cov$RIN)
```

#TRIM26

```{r }
riskVar <- read_tsv("~/BTSync/FetalRNAseq/Genotypes/rs2021722.txt", col_names=FALSE)
colnames(riskVar) <- c('chr', 'pos', 'riskVar', 'BrainBankID')
counts<- allCounts[,c(1, 79:155)] %>%
  filter(Id =='ENSG00000234127.8') %>%
  gather(sample, count, -Id) %>%
  separate(sample, c('norm', 'BrainBankID'), sep='\\.') %>%
  left_join(riskVar) %>%
  mutate(riskVar = ifelse(riskVar == 'T|C', 'C|T', as.character(riskVar)))

ggplot(counts, aes(x=riskVar, y=count)) +
  geom_jitter(alpha=.2, height=0, width=.25) +
  tufte_theme()

summary(lm(count ~ riskVar, data=counts))
```

## Co-variates
`r margin_note("- None of co-variates are significant")`

```{r}
count_cov <- counts %>% left_join(covariates) 
ggplot(count_cov, aes(x=PCW, y=count)) + geom_point(alpha=.2) +
  tufte_theme()
ggplot(count_cov, aes(x=Sex, y=count)) +   geom_jitter(alpha=.2, height=0, width=.25) +
  tufte_theme()
ggplot(count_cov, aes(x=RIN, y=count)) + geom_point(alpha=.2) +
  tufte_theme()

summary(lm(count ~ PCW + Sex +RIN, data=count_cov))
summary(lm(count ~ PCW, data=count_cov))
summary(lm(count ~ Sex, data=count_cov))
summary(lm(count ~ RIN, data=count_cov))
cor.test(count_cov$count, count_cov$PCW)
cor.test(count_cov$count, count_cov$RIN)
```

#CSMD1

```{r }
riskVar <- read_tsv("~/BTSync/FetalRNAseq/Genotypes/rs10503253.txt", col_names=FALSE)
colnames(riskVar) <- c('chr', 'pos', 'riskVar', 'BrainBankID')
counts<- allCounts[,c(1, 79:155)] %>%
  filter(Id =='ENSG00000183117.17') %>%
  gather(sample, count, -Id) %>%
  separate(sample, c('norm', 'BrainBankID'), sep='\\.') %>%
  left_join(riskVar) %>%
  mutate(riskVar = ifelse(riskVar == 'C|A', 'A|C', as.character(riskVar)))

ggplot(counts, aes(x=riskVar, y=count)) +
  geom_jitter(alpha=.2, height=0, width=.25) +
  tufte_theme()

summary(lm(count ~ riskVar, data=counts))
```

## Co-variates
`r margin_note("- None of co-variates are significant")`

```{r}
count_cov <- counts %>% left_join(covariates) 
ggplot(count_cov, aes(x=PCW, y=count)) + geom_point(alpha=.2) +
  tufte_theme()
ggplot(count_cov, aes(x=Sex, y=count)) +   geom_jitter(alpha=.2, height=0, width=.25) +
  tufte_theme()
ggplot(count_cov, aes(x=RIN, y=count)) + geom_point(alpha=.2) +
  tufte_theme()

summary(lm(count ~ PCW + Sex +RIN, data=count_cov))
summary(lm(count ~ PCW, data=count_cov))
summary(lm(count ~ Sex, data=count_cov))
summary(lm(count ~ RIN, data=count_cov))
cor.test(count_cov$count, count_cov$PCW)
cor.test(count_cov$count, count_cov$RIN)
```

#MMP16

```{r }
riskVar <- read_tsv("~/BTSync/FetalRNAseq/Genotypes/rs7004633.txt", col_names=FALSE)
colnames(riskVar) <- c('chr', 'pos', 'riskVar', 'BrainBankID')
counts<- allCounts[,c(1, 79:155)] %>%
  filter(Id =='ENSG00000156103.15') %>%
  gather(sample, count, -Id) %>%
  separate(sample, c('norm', 'BrainBankID'), sep='\\.') %>%
  left_join(riskVar) %>%
  mutate(riskVar = ifelse(riskVar == 'G|A', 'A|G', as.character(riskVar)))

ggplot(counts, aes(x=riskVar, y=count)) +
  geom_jitter(alpha=.2, height=0, width=.25) +
  tufte_theme()

summary(lm(count ~ riskVar, data=counts))
```

## Co-variates
`r margin_note("- Sex is highely significant")`

```{r}
count_cov <- counts %>% left_join(covariates) 
ggplot(count_cov, aes(x=PCW, y=count)) + geom_point(alpha=.2) +
  tufte_theme()
ggplot(count_cov, aes(x=Sex, y=count)) +   geom_jitter(alpha=.2, height=0, width=.25) +
  tufte_theme()
ggplot(count_cov, aes(x=RIN, y=count)) + geom_point(alpha=.2) +
  tufte_theme()

summary(lm(count ~ PCW + Sex +RIN, data=count_cov))
summary(lm(count ~ PCW, data=count_cov))
summary(lm(count ~ Sex, data=count_cov))
summary(lm(count ~ RIN, data=count_cov))
cor.test(count_cov$count, count_cov$PCW)
cor.test(count_cov$count, count_cov$RIN)
```

#CNNM2

```{r }
riskVar <- read_tsv("~/BTSync/FetalRNAseq/Genotypes/rs7914558.txt", col_names=FALSE)
colnames(riskVar) <- c('chr', 'pos', 'riskVar', 'BrainBankID')
counts<- allCounts[,c(1, 79:155)] %>%
  filter(Id =='ENSG00000148842.17') %>%
  gather(sample, count, -Id) %>%
  separate(sample, c('norm', 'BrainBankID'), sep='\\.') %>%
  left_join(riskVar) %>%
  mutate(riskVar = ifelse(riskVar == 'G|A', 'A|G', as.character(riskVar)))

ggplot(counts, aes(x=riskVar, y=count)) +
  geom_jitter(alpha=.2, height=0, width=.25) +
  tufte_theme()

summary(lm(count ~ riskVar, data=counts))
```

## Co-variates
`r margin_note("- RIN is highely significant")`

```{r}
count_cov <- counts %>% left_join(covariates) 
ggplot(count_cov, aes(x=PCW, y=count)) + geom_point(alpha=.2) +
  tufte_theme()
ggplot(count_cov, aes(x=Sex, y=count)) +   geom_jitter(alpha=.2, height=0, width=.25) +
  tufte_theme()
ggplot(count_cov, aes(x=RIN, y=count)) + geom_point(alpha=.2) +
  tufte_theme()

summary(lm(count ~ PCW + Sex +RIN, data=count_cov))
summary(lm(count ~ PCW, data=count_cov))
summary(lm(count ~ Sex, data=count_cov))
summary(lm(count ~ RIN, data=count_cov))
cor.test(count_cov$count, count_cov$PCW)
cor.test(count_cov$count, count_cov$RIN)
```

#NT5C2
`r margin_note("- Not present in HTSeq-count output")`

#STT3A

```{r }
riskVar <- read_tsv("~/BTSync/FetalRNAseq/Genotypes/rs548181.txt", col_names=FALSE)
colnames(riskVar) <- c('chr', 'pos', 'riskVar', 'BrainBankID')
counts<- allCounts[,c(1, 79:155)] %>%
  filter(Id =='ENSG00000134910.12') %>%
  gather(sample, count, -Id) %>%
  separate(sample, c('norm', 'BrainBankID'), sep='\\.') %>%
  left_join(riskVar) %>%
  mutate(riskVar = ifelse(riskVar == 'G|A', 'A|G', as.character(riskVar)))

ggplot(counts, aes(x=riskVar, y=count)) +
  geom_jitter(alpha=.2, height=0, width=.25) +
  tufte_theme()

summary(lm(count ~ riskVar, data=counts))
```

## Co-variates
`r margin_note("- PCW is marginally significant")`

```{r}
count_cov <- counts %>% left_join(covariates) 
ggplot(count_cov, aes(x=PCW, y=count)) + geom_point(alpha=.2) +
  tufte_theme()
ggplot(count_cov, aes(x=Sex, y=count)) +   geom_jitter(alpha=.2, height=0, width=.25) +
  tufte_theme()
ggplot(count_cov, aes(x=RIN, y=count)) + geom_point(alpha=.2) +
  tufte_theme()

summary(lm(count ~ PCW + Sex +RIN, data=count_cov))
summary(lm(count ~ PCW, data=count_cov))
summary(lm(count ~ Sex, data=count_cov))
summary(lm(count ~ RIN, data=count_cov))
cor.test(count_cov$count, count_cov$PCW)
cor.test(count_cov$count, count_cov$RIN)
```

#CCDC68

```{r }
riskVar <- read_tsv("~/BTSync/FetalRNAseq/Genotypes/rs12966547.txt", col_names=FALSE)
colnames(riskVar) <- c('chr', 'pos', 'riskVar', 'BrainBankID')
counts<- allCounts[,c(1, 79:155)] %>%
  filter(Id =='ENSG00000166510.13') %>%
  gather(sample, count, -Id) %>%
  separate(sample, c('norm', 'BrainBankID'), sep='\\.') %>%
  left_join(riskVar) %>%
  mutate(riskVar = ifelse(riskVar == 'G|A', 'A|G', as.character(riskVar)))

ggplot(counts, aes(x=riskVar, y=count)) +
  geom_jitter(alpha=.2, height=0, width=.25) +
  tufte_theme()

summary(lm(count ~ riskVar, data=counts))
```

## Co-variates
`r margin_note("- None of co-variates are significant")`

```{r}
count_cov <- counts %>% left_join(covariates) 
ggplot(count_cov, aes(x=PCW, y=count)) + geom_point(alpha=.2) +
  tufte_theme()
ggplot(count_cov, aes(x=Sex, y=count)) +   geom_jitter(alpha=.2, height=0, width=.25) +
  tufte_theme()
ggplot(count_cov, aes(x=RIN, y=count)) + geom_point(alpha=.2) +
  tufte_theme()

summary(lm(count ~ PCW + Sex +RIN, data=count_cov))
summary(lm(count ~ PCW, data=count_cov))
summary(lm(count ~ Sex, data=count_cov))
summary(lm(count ~ RIN, data=count_cov))
cor.test(count_cov$count, count_cov$PCW)
cor.test(count_cov$count, count_cov$RIN)
```

#TCF4

```{r }
riskVar <- read_tsv("~/BTSync/FetalRNAseq/Genotypes/rs17512836.txt", col_names=FALSE)
colnames(riskVar) <- c('chr', 'pos', 'riskVar', 'BrainBankID')
counts<- allCounts[,c(1, 79:155)] %>%
  filter(Id =='ENSG00000196628.13') %>%
  gather(sample, count, -Id) %>%
  separate(sample, c('norm', 'BrainBankID'), sep='\\.') %>%
  left_join(riskVar) %>%
  mutate(riskVar = ifelse(riskVar == 'T|C', 'C|T', as.character(riskVar)))

ggplot(counts, aes(x=riskVar, y=count)) +
  geom_jitter(alpha=.2, height=0, width=.25) +
  tufte_theme()

summary(lm(count ~ riskVar, data=counts))
```

## Co-variates
`r margin_note("- PCW is highely significant")`

```{r}
count_cov <- counts %>% left_join(covariates) 
ggplot(count_cov, aes(x=PCW, y=count)) + geom_point(alpha=.2) +
  tufte_theme()
ggplot(count_cov, aes(x=Sex, y=count)) +   geom_jitter(alpha=.2, height=0, width=.25) +
  tufte_theme()
ggplot(count_cov, aes(x=RIN, y=count)) + geom_point(alpha=.2) +
  tufte_theme()

summary(lm(count ~ PCW + Sex +RIN, data=count_cov))
summary(lm(count ~ PCW, data=count_cov))
summary(lm(count ~ Sex, data=count_cov))
summary(lm(count ~ RIN, data=count_cov))
cor.test(count_cov$count, count_cov$PCW)
cor.test(count_cov$count, count_cov$RIN)
```

